PREVIC: An adaptive parent report measure of expressive vocabulary in children between 3 and 8 years of age

### 2024-11-07 paper/manuscript.tex
revision

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

@@

The task can be accessed via the following website: \url{https://ccp-odc.eva.mpg.de/previc-demo/}. The corresponding source code can be found in the following repository: \url{https://github.com/ccp-eva/previc-demo}. The data sets generated during and/or analysed during the current study are available in the following repository: \url{https://github.com/ccp-eva/previc/}. Data collection was preregistered at: \url{https://osf.io/utzfh}.

>>>>

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

@@

The task can be accessed via the following website: \url{https://ccp-odc.eva.mpg.de/previc-demo/}. The corresponding source code can be found in the following repository: \url{https://github.com/ccp-eva/previc-demo}. The data sets generated during and/or analysed during the current study are available in the following repository: \url{https://github.com/manuelbohn/previc/}. Data collection was preregistered at: \url{https://osf.io/utzfh}.
